What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Usage metric fixes

In total, \kaggleAllcalls \eval were recorded, all to \eval function. Out of
\kaggleStaticeval sites from \KaggleWithEvals, only \kaggleTriggeredeval sites
in \kaggleNbruns scripts were hit; \KaggleFailedScripts scripts failed to run,
and the other did not exercise the \eval sites. This is partially expected
as Kaggle code does not need to abide by any checks. Upon a manual inspection,
we observed that indeed the failing scripts were of poor quality, often not
finished, using misspelled package names, hard-coded file paths, or accessing
missing files.

>>>>

In total, \kaggleAllcalls \eval were recorded, all to \eval function. Out of
\kaggleStaticeval sites from \KaggleWithEvals scripts, only \kaggleTriggeredeval sites
in \kaggleNbruns scripts were hit; \KaggleFailedScripts scripts failed to run,
and the others did not exercise the \eval sites. This is partially expected
as Kaggle code does not need to abide by any checks. Upon a manual inspection,
we observed that indeed, the failing scripts were of poor quality, often not
finished, using misspelled package names, hard-coded file paths, or accessing
missing files.
